HPC--101\\Onboarding

### 2023-06-22 hpc_101/sections/01_intro.tex
Added information about Mana migration to Koa

\section[University of Hawai'i High Performance Compute Cluster]{University of Hawai'i High Performance Compute Cluster}
\begin{frame}
    \frametitle{University of {\hawaii} High Performance Compute Cluster}
    \begin{itemize}
    \item The University~of~{\hawaii} High Performance Compute Cluster - \textbf{\mana} is \textbf{free} to use for all active faculty, staff, and students affiliated with the University of {\hawaii}
    \item Community acquired nodes are equally accessible to all users
    \item Nodes purchased through the {\textbf{condo program}} are shared with the community, but priority is given to the node owner and their agents
		\item Nodes may be {\textbf{leased}} from the community pool
		\item Additional permanent storage can be leased by faculty \& staff
    \end{itemize}
		\begin{block}{Mana Resource Summary}
  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||l||l||l||l||l||l||l}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
			\toprule

              {}               & \thead{\textbf{Nodes}} & \thead{\textbf{CPU Cores}} & \thead{\textbf{Memory}} & \thead{\textbf{GPUs}} & \thead{\textbf{Home/Group Space}} & \thead{\textbf{Scratch Space}} & \thead{\textbf{Storage for lease}} \\ 
							\midrule  \midrule %\hline
        \thead{\textbf{Total}} & 366                    & 9,396                      & 67.3 TB                   &  120                   & 80 TB                             &  111 TB                        & 1 PB              \\ %\hline
				\bottomrule
      \end{tabular}%
    }
  \end{table}
	\end{block}
\end{frame}

@@

>>>>

\section[University of Hawai'i High Performance Compute Cluster]{University of Hawai'i High Performance Compute Cluster}
\begin{frame}
    \frametitle{University of {\hawaii} High Performance Compute Cluster}
    \begin{itemize}
    \item The University~of~{\hawaii} High Performance Compute Cluster - \textbf{\mana} is \textbf{free} to use for all active faculty, staff, and students affiliated with the University of {\hawaii}
    \item Community acquired nodes are equally accessible to all users
    \item Nodes purchased through the {\textbf{condo program}} are shared with the community, but priority is given to the node owner and their agents
    \itmem Mana is currently undergoing a migration, resource summary subject to change. 
		\item Nodes may be {\textbf{leased}} from the community pool
		\item Additional permanent storage can be leased by faculty \& staff
    \end{itemize}
		\begin{block}{Mana Resource Summary\footnotemark}
  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||l||l||l||l||l||l||l}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
			\toprule

              {}               & \thead{\textbf{Nodes}} & \thead{\textbf{CPU Cores}} & \thead{\textbf{Memory}} & \thead{\textbf{GPUs}} & \thead{\textbf{Home/Group Space}} & \thead{\textbf{Scratch Space}} & \thead{\textbf{Storage for lease}} \\ 
							\midrule  \midrule %\hline
        \thead{\textbf{Total}} & 366                    & 9,396                      & 67.3 TB                   &  120                   & 80 TB                             &  111 TB                        & 1 PB              \\ %\hline
				\bottomrule
      \end{tabular}%
    }
  \end{table}
	\end{block}
 \footnotetext{Mana is currently undergoing a migration, resource summary subject to change over the next few months.}
\end{frame}

@@

\begin{frame}
  \frametitle{Permanent Storage }
  \begin{enumerate}
  \item Long Term Storage (LTS)
    \begin{itemize}
    \item {\textbf{Purpose}}: \footnotesize Additional Personal and/or group storage for applications and active data when all other storage options have been exhausted in {\mana}\footnote{\label{LTS}\tiny\ \url{https://hawaii.kualibuild.com/app/builder/app/6062a8170d0d97001cb7d3af/run}}

    \end{itemize}
  \end{enumerate}
~\\
  LTS storage on {\mana} has the following attributes:
  \begin{itemize}
  \item \$20/TB with a minimum purchase of 2TB 
  \item LTS purchases are done in a per year basis
  \item Available on all nodes
  \end{itemize}

\begin{frame}
  \frametitle{Mana Migration}
~\\
  The new Mana/Koa cluster will have the following attributes:
  \begin{itemize}
	  \item {\textbf{Storage}}: New separate storage system. Files will need to be migrated, and files remaining in Mana will be deleted once the old cluster is turned off. 
	  \item{\textbf{Home}}:Permanent storage with 50GB quota for personal applications and data
	  \item{\textbf{Scratch}}: 800 TB and 400,000,000 file quota shared across all users with a 90 day purge policy. 
  \item{\textbf{Workspace}}: Factulty and staff members will allocated 1TB of workspace upon request, to be shared by lab and group members. 
  \item {\textbf{Timeline}}: Progressive migration in 6 differnt stages \footnotemark
  \end{itemize}
  \footnotetext{\tiny\url{https://datascience.hawaii.edu/mana-upgrade/}}
